### 2024-03-26 manuscript/manuscript.qmd
fix Table formatting

#### **Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis**

@@

```{r}
#| tab.id: table3
#| results: markup
pilot_main_eff_ddm_table
```

@@

```{r}
#| tab.id: table4
#| results: markup
study1_results_table
```

@@

```{r}
#| tab.id: table5
#| results: markup
study1_condition_results_table
```

>>>>

#### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**

@@

```{r}
#| tab.id: table3
#| results: markup
pilot_main_eff_ddm_table |> 
  border(i = 1, border.bottom = fp_border_default(), part = "header") 
```

@@

```{r}
#| tab.id: table4
#| results: markup
study1_results_table |> 
  border(i = 1, border.bottom = fp_border_default(), part = "header") 
```

@@

```{r}
#| tab.id: table5
#| results: markup
study1_condition_results_table |> 
  border(i = 1, border.bottom = fp_border_default(), part = "header") 
```
